Chr2 hotspot preliminary analyses

### 2019-06-27 analysis/paper/Chr11-prelim.Rmd
added threshold values to tibbles

    my_other_list[[j]] <- foo %>%
      mutate(med = lod_diff > med_vals[i], pleio = pleiotropy_lod <= pleio_vals[j]) %>%
      group_by(med, pleio) %>%
      count() %>%
      left_join(uniq_cts, by = c("med", "pleio"))
  }
  mylist[[i]] <- my_other_list
} 
mylist
```

```{r}
mylist %>%
  map_df(bind_rows)
```

>>>>

    my_other_list[[j]] <- foo %>%
      mutate(med = lod_diff > med_vals[i], pleio = pleiotropy_lod <= pleio_vals[j]) %>%
      group_by(med, pleio) %>%
      count() %>%
      left_join(uniq_cts, by = c("med", "pleio")) %>%
      mutate(med_thr = med_vals[i], pleio_thr = pleio_vals[j])
  }
  mylist[[i]] <- my_other_list
} 
mylist
```
```{r}
mylist %>%
  map_df(bind_rows)
```

### 2019-06-27 analysis/paper/Chr2-prelim.Rmd
added threshold values to tibbles

    my_other_list[[j]] <- foo %>%
      mutate(med = lod_diff > med_vals[i], pleio = pleiotropy_lod <= pleio_vals[j]) %>%
      group_by(med, pleio) %>%
      count() %>%
      left_join(uniq_cts, by = c("med", "pleio"))
  }
  mylist[[i]] <- my_other_list
} 
mylist
```

>>>>

    my_other_list[[j]] <- foo %>%
      mutate(med = lod_diff > med_vals[i], pleio = pleiotropy_lod <= pleio_vals[j]) %>%
      group_by(med, pleio) %>%
      count() %>%
      left_join(uniq_cts, by = c("med", "pleio")) %>%
      mutate(med_thr = med_vals[i], pleio_thr = pleio_vals[j])
  }
  mylist[[i]] <- my_other_list
} 
mylist
```
